---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```




```{r bibdata, include=FALSE}
library(bibliometRics)
wos_file = system.file("sbegueria.txt", package = "bibliometRics")
bib <- read.wos(wos_file)
quant <- read.baselines()
x <- bibliometric(bib, quant, 'GEOSCIENCES')
publist <- apply(
  cbind(bib$pubs,
        citation_rank(bib, quant = quant$GEOSCIENCES)), 
  1, format_pub, au =
    bib$au)
bib$ref
bib$au
```



## Indicators

```{r biblioplot, cairo-scatter, echo=FALSE, message=FALSE, warning=FALSE,  fig.width=12, fig.height=4}
biblioplot(bib, quant =  quant$GEOSCIENCES)
```


## Table

\begin{table}[h]
\centering
\begin{tabular}{llll}
\hline
Publications (total) & Pubs. (as lead author) & Years & Pubs. per year \\
`r x$pubs` & `r x$lead` & `r x$years` & `r x$pubs_year` \\
\hline
Citations (total) & Citations per year & Citations per pub & Citations (highest pub) \\
`r x$cit_tot` & `r x$cit_year` & `r x$cit_art` & `r x$cit_max` \\
\hline
h-index & h-index per year & g-index & g-index per year \\
`r x$hin` & `r x$hin_year` & `r x$gin` & `r x$gin_year` \\
\hline
Pubs $>$q0.9 & Pubs $>$q0.9 (as lead) & i-score & i-score (as lead) \\
`r x$pubs09` & `r x$pubs09_lead` & `r x$iscore` & `r x$iscore_lead` \\
\hline
\end{tabular}
\end{table}


# Publication list

\begin{enumerate}
`r publist`
\end{enumerate}


\end{document}
